---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/readme/"
)
```

[![Travis-CI Build Status](https://travis-ci.org/ateucher/lutz.svg?branch=master)](https://travis-ci.org/ateucher/lutz) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/ateucher/lutz?branch=master&svg=true)](https://ci.appveyor.com/project/ateucher/lutz) [![Coverage Status](https://img.shields.io/codecov/c/github/ateucher/lutz/master.svg)](https://codecov.io/github/ateucher/lutz?branch=master)

# lutz (look up timezones)

Input latitude and longitude values or an `sf/sfc` POINT object and get back 
the timezone in which they exist. Two methods are implemented. One is very 
fast and uses an Rcpp in conjunction with source data from (https://github.com/darkskyapp/tz-lookup/). 
However, speed comes at the cost of accuracy - near time zone borders away from 
populated centres there is a chance that it will return the incorrect time zone. 

The other method is slower but more accurate - it uses the sf package to 
intersect points with a detailed map of time zones from 
[here](https://github.com/evansiroky/timezone-boundary-builder).

## Installation

You can install lutz from CRAN with:

```{r eval=FALSE}
install.packages("lutz")
```

Or you can install the development version from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ateucher/lutz")
```

## Examples

There are only two functions in this package: `tz_lookup()` which works with both `sf/sfc` and `SpatialPoints` objects, and `tz_lookup_coords` for looking up lat/long pairs. Use the `method` argument to choose the `"fast"` or `"accurate"`
method.

### With coordinates. They must be lat/long in decimal degrees:
```{r warning=FALSE}
library(lutz)
tz_lookup_coords(49.5, -123.5, method = "fast")
tz_lookup_coords(49.5, -123.5, method = "accurate")

tz_lookup_coords(lat = c(48.9, 38.5, 63.1, -25), lon = c(-123.5, -110.2, -95.0, 130))
```

### With `sf` objects:
```{r warning=FALSE, message=FALSE}
library(sf)
library(ggplot2) # this requires the devlopment version of ggplot2

# Create an sf object out of the included state.center dataset:
pts <- lapply(seq_along(state.center$x), function(i) {
  st_point(c(state.center$x[i], state.center$y[i]))
})
state_centers_sf <- st_sf(st_sfc(pts))

# Use tz_lookup_sf to find the timezones
state_centers_sf$tz <- tz_lookup(state_centers_sf)
state_centers_sf$tz <- tz_lookup(state_centers_sf, method = "accurate")

ggplot() + 
  geom_sf(data = state_centers_sf, aes(colour = tz)) + 
  theme_minimal() + 
  coord_sf(datum = NA)
```

### With `SpatialPoints` objects:
```{r warning=FALSE}
library(sp)
state_centers_sp <- as(state_centers_sf, "Spatial")

state_centers_sp$tz <- tz_lookup(state_centers_sp)

ggplot(cbind(as.data.frame(coordinates(state_centers_sp)), tz = state_centers_sp$tz), 
       aes(x = coords.x1, y = coords.x2, colour = tz)) + 
  geom_point() + 
  coord_fixed() + 
  theme_minimal()
```


We can compare the accuracy of both methods to the high-resolution timezone map
provided by https://github.com/evansiroky/timezone-boundary-builder. This is the
map that is used by `lutz` for the `"accurate"` method, but in `lutz` it is 
simplified by about 80% to be small enough to fit in the package.

```{r eval=FALSE}
## Get the full timezone geojson from https://github.com/evansiroky/timezone-boundary-builder
download.file("https://github.com/evansiroky/timezone-boundary-builder/releases/download/2018d/timezones-with-oceans.geojson.zip",
                destfile = "tz.zip")
unzip("tz.zip", exdir = "data-raw/dist/")
```


```{r eval=file.exists("data-raw/dist/combined-with-oceans.json")}
library(lutz)
library(sf)
library(rmapshaper)
library(purrr)

tz_full <- read_sf("data-raw/dist/combined-with-oceans.json")
# Create a data frame of 500000 lat/long pairs:
set.seed(1)
n <- 500000
ll <- data.frame(lat = runif(n, -90, 90), lon = runif(n, -180, 180))
ll_sf <- st_as_sf(ll, coords = c("lon", "lat"), crs = 4326)

# Overlay those points with the full high-resolution timezone map:
ref_ll_tz <- sf::st_join(ll_sf, tz_full)

# run tz_lookup with both `"fast"` and `"accurate"` methods and compare with 
# the timezones looked up with the high-resolution map:
tests <- map_df(c("fast", "accurate"), ~ {
  time <- system.time(test_ll_tz <- tz_lookup(ll_sf, method = .x, warn = FALSE))
  comp <- ref_ll_tz$tzid == test_ll_tz
  matches <- sum(comp, na.rm = TRUE)
  mismatches <- sum(!comp, na.rm = TRUE)
  list(
    method = .x,
    time = time["elapsed"],
    matches = matches,
    mismatches = mismatches,
    accuracy = matches / (matches + mismatches),
    ref_nas = sum(is.na(ref_ll_tz$tzid)),
    fun_nas = sum(is.na(test_ll_tz))
    )
})
```

```{r results="asis", eval=file.exists("data-raw/dist/combined-with-oceans.json")}
knitr::kable(tests)
```
